To log or not to log

### 2022-01-28 main.tex

@@

\section{Introduction}

@@

\paragraph{What we propose}
Proper scoring rules yield a score as a function of a forecast $x$ and a corresponding observation $y$. For epidemiological forecasts of positive quantities we propose to replace WIS and CRPS scores on the natural scale computed as 
%
\begin{equation}
S(x, y),     
\end{equation}
%
by scores computed on the logarithmic scale as 
%
\begin{equation}
S(\log{(x + 1)}, \log{(y + 1)}),    
\end{equation}
%
where $S()$ is either the WIS or the CRPS and one is added to deal with zeros in the data. The so computed score is still proper, as for a single forecast the order between different forecasters is not affected by the monotone transformation. Differences in the ranking between forecasters only appear when averaging over multiple forecasts, as deviations from the perfect forecast get penalised differently depending on whether forecasts are scored on the log or the natural scale. Note that simply taking the log of a score computed on the natural scale, i.e. computing $\log S(x, y)$ results in an improper score and is therefore not advised. We illustrate this point in Figure \ref{fig:log-improper} in the SI.

@@

>>>>

\tableofcontents

@@

% Introduction
%    - Role of forecasts and problems in comparing them
%    - Introduction to scoring rules, WIS, CRPS
%    - outline of the paper
%Scoring on a log scale
%    - what we propose
%    - we approximately score the growth rate
%    - focus is shifted from additive to multiplicative error
%    - Interpretation: 
%        - How do forecast weights change: what gets high and %what gets low scores? 
%        - - Figure from Johannes: How CRPS changes when you log %the observation
%
%Appropriate scales for epidemiological processes
%    - general point about how all processes are modelled %multiplicatively and therefore it might be odd to score them %based on absolute errors
%    - Simulations Sam? 
%    - Adding up several districts - how do scores change? %(Example Johannes) --> relationship between mean and variance %in scores
%
%Example: European Forecast Hub: 
%    - paragraph introduction to the Forecast Hub
%    - How does the distribution of scores change
%        - target types, locations, over time
%    - relationship between mean and sd of WIS

% ===========================================================
\section{Introduction}

@@

\paragraph{What we propose}
Proper scoring rules yield a score as a function of a forecast $x$ and a corresponding observation $y$. For epidemiological forecasts of positive quantities we propose to replace WIS and CRPS scores on the natural scale computed as 
%
\begin{equation}
S(x, y),     
\end{equation}
%
by scores computed on the logarithmic scale as 
%
\begin{equation}
S(\log{(x + 1)}, \log{(y + 1)}),    
\end{equation}
%
where $S()$ is either the WIS or the CRPS and one is added to deal with zeros in the data. The so computed score is still proper, as for a single forecast the order between different forecasters is not affected by the monotone transformation.
% last sentence not very clear
Differences in the ranking between forecasters only appear when averaging over multiple forecasts, as deviations from the perfect forecast get penalised differently depending on whether forecasts are scored on the log or the natural scale. Note that simply taking the log of a score computed on the natural scale, i.e. computing $\log S(x, y)$ results in an improper score and is therefore not advised. We illustrate this point in Figure \ref{fig:log-improper} in the SI. 
% ADD A COMMENT ABOUT LOG X + 1

@@

\section{Empirical example: the European Forecast Hub}

\paragraph{Introduction to the Forecast Hub}

NEED A TABLE WITH SCORES

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-average-scores.png}
    \caption{CAPTION}
    \label{fig:HUB-average-scores}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-scores-locations.png}
    \caption{CAPTION}
    \label{fig:HUB-scores-location}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-scores-over-horizon.png}
    \caption{CAPTION}
    \label{fig:HUB-scores-horizon}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-scores-over-time.png}
    \caption{CAPTION}
    \label{fig:HUB-scores-time}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-sd-vs-mean-scores.png}
    \caption{CAPTION}
    \label{fig:HUB-mean-sd-scores}
\end{figure}
